Comparison to Christensen et al. 2018

### 2019-02-11 doc/paper-comparison.Rmd
Build vignettes on RMD's machine

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

@@

@@

```{r, eval = T}
library(LDATS)

@@

```{r download Christensen}

paper_filepath <- here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files')
test_filepath <- here::here('vignettes', 'christensenetal-ristensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_LDA_analysis.r')

@@

```{r LDATS data}

data(rodents)

head(rodents[[1]])

@@

```{r Paper data}
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_data_for_LDA.r'))

@@

```{r adjust LDATS data after Christensen et al}

trap_table = read.csv('https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/Portal_rodent_trapping.csv')
  trap_table_controls =dplyr::filter(trap_table, plot %in% c(2,4,8,11,12,14,17,22))
  nplots_controls = aggregate(trap_table_controls$sampled,by=list(period = trap_table_controls$period),FUN=sum)

   # adjust species counts by number of plots trapped that month
  ldats_rodents_adjusted = as.data.frame.matrix(rodents[[1]])
  for (n in 1:436) {
    #divide by number of control plots actually trapped (should be 8) and multiply by 8 to estimate captures as if all plots were trapped
    ldats_rodents_adjusted[n,] = round(ldats_rodents_adjusted[n,]/nplots_controls$x[n]*8)
  }

@@

```{r rm LDATS LDAS, include = F, eval = F}
rm(list = c('ldats_ldas', 'ldats_lda_selected'))
```

@@

```{r cleanup paper LDAS, include = F, eval = F}
rm(list = c('dat', 'ldamodel', 'max_dist', 'mean_dist',
            'ntopics', 'SEED', 'seeds', 'seeds_4topics', 'aic_model', 'aic_model_gibbs', 'calculate_LDA_distance', 'Hellinger', 'min_H', 'repeat_VEM', 'best_ntopic', 'best_seed'))
```

```{r reload LDAS, include = FALSE}

load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))

@@

#### Paper LDA
```{r plot paper LDA, fig.width=6, fig.height=6}
# Paper
plot(ldamodel, cols = NULL, option = "D")

#### LDATS LDA
```{r plot LDATS LDA, fig.width=6, fig.height=6}
# LDATS
plot(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

```{r remove LDAS after plotting, include = F}
rm(ldamodel)
rm(ldats_lda_selected)
```

@@

```{r load LDATS LDA for paper cpt}

#### Load LDA ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))
rm(cp_results_rodent6)
```

```{r select LDATS LDA and paper cpt}
#### Changepoint model selection ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))

ntopics = ldats_lda_selected[[1]]@k

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

@@

df_4 = as.data.frame(t(cp_results_rodent4$saved[,1,])) %>% reshape::melt()
year_continuous = 1970 + as.integer(julian(paper_dates)) / 365.25
df_4$value = year_continuous[df_4$value]

@@

```{r clean up LDATS LDA and paper changepoint, include = F}
rm(list = c('cp_results_rodent', 'cp_results_rodent2', 'cp_results_rodent3', 'cp_results_rodent4', 'cp_results_rodent5', 'cp_results_rodent6', 'ntopics', 'ldats_lda_selected', 'df_4'))
```

@@

```{r load paper LDA for paper cpt}

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper1.Rds'))
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper2.Rds'))
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper3.Rds'))
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper4.Rds'))
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper5.Rds'))
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper6.Rds'))
rm(cp_results_rodent6)
```

```{r select paper LDA and paper cpt}
#### Changepoint model selection ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_1.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_2.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_3.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_5.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_6.Rds'))

ntopics = ldamodel@k

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

@@

df_4 = as.data.frame(t(cp_results_rodent4$saved[,1,])) %>%  reshape::melt()
df_4$value = year_continuous[df_4$value]

@@

```{r clean up paper LDA and paper changepoint, include = F}
rm(list = c('cp_results_rodent', 'cp_results_rodent2', 'cp_results_rodent3', 'cp_results_rodent4', 'cp_results_rodent5', 'cp_results_rodent6', 'ntopics', 'ldamodel', 'df_4'))
```

@@

```{r load LDATS LDA for LDATS cpt}

#### Load LDA ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))

@@

ldats_ldats_cpt <- TS_on_LDA(LDA_models = ldats_lda_selected, 
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             weights = NULL)

@@

```{r load LDATS LDA and LDATS changepoint, include = F}
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats.Rds'))
```

@@

```{r cleanup LDATS LDA and LDATS changepoint, include = F}

save(ldats_ldats_cpt_selected, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats_selected.Rds'))

rm(ldats_ldats_cpt_selected)
rm(ldats_ldats_cpt)
```

@@

```{r load paper LDA for LDATS cpt}

@@

paper_ldats_cpt <- TS_on_LDA(LDA_models = ldamodel, 
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             weights = NULL)

@@

```{r load paper LDA and LDATS changepoint, include = F}
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats.Rds'))
```

@@

```{r cleanup paper LDA and LDATS changepoint, include = F}

save(paper_ldats_cpt_selected, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats_selected.Rds'))

rm(paper_ldats_cpt_selected)
rm(paper_ldats_cpt)
rm(list = c('newdate', 'halfinterval'))
```

@@

```{r load cpts to plot, include = F}
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats_selected.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats_selected.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
paper_paper_cpt_selected <- cp_results_rodent4
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
ldats_paper_cpt_selected <- cp_results_rodent4

@@

```{r plot paper LDA and LDATS cpts, fig.width=6, fig.height=6}

@@

#### LDATS LDA and LDATS changepoint
```{r plot ldats LDA and LDATS cpt, fig.width=6, fig.height=6}
plot(ldats_ldats_cpt_selected)
```

#### Paper LDA and paper changepoint
```{r plot paper LDA and paper cpt, fig.width=6, fig.height=6}

@@

#### LDATS LDA and paper changepoint
```{r plot LDATS lda and paper cpt, fig.width=6, fig.height=6}
ntopics = 6
ldats_cpts = find_changepoint_location(ldats_paper_cpt_selected)
ldats_cpt_plot = get_ll_non_memoized_plot(ldats_lda_selected[[1]],x,ldats_cpts,make_plot=T,weights=rep(1,length(year_continuous)))
annual_hist(ldats_paper_cpt_selected, year_continuous)
ldats_cpt_plot
```

@@

```{r cleanup cpt_dates, include = F}
rm(list= 'ldats_ldats_cpt_dates', 'ldats_paper_cpt_dates',  'paper_ldats_cpt_dates', 'paper_paper_cpt_dates', 'cpt_dates')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

@@

## Summary

| Step | Changes from Christensen et al 2018 to `LDATS` | Effect on comparison | Recommendations for future users |
|:---------------|:------------------------|:-----------------------|:----------------------------|
|Data|Paper adjusts abundances according to unit effort, while `LDATS` uses raw capture numbers.|None: run comparison using adjusted data|Use raw, unweighted abundances.|
|LDA model selection|Paper conservatively overestimated the number of parameters for calculating AIC for model selection. `LDATS` calculates AIC appropriately.|Paper LDA selects 4 topics, while `LDATS` finds 6. Compare all combinations of paper and `LDATS` LDA models and changepoint models| Use `LDATS` AIC calculation.|
|Changepoint model document weights|Paper weighted all sampling periods equally regardless of abundance. `LDATS` by default weights the information from each sampling period according to the number of individuals captured (i.e. the amount of information gleaned about the underlying community composition).|None; use `weights = NULL` to set all weights equal to 1 for LDATS| Weight sampling periods according to abundance|
|Overall LDA + changepoint results| All combinations of LDA + changepoint model find 4 changepoints at approximately the same time steps|Choice of LDA model has more of an effect than choice of changepoint model|`LDATS` reflects best practices, but the paper methods produced qualitatively similar results.|

@@

```{r, eval = T}
library(LDATS)
library(dplyr)
load(here::here('vignettes', 'christensenetal-comparison-files',  'data_files.Rdata'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache',  'ldas.RData'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_changepoints.RData'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_changepoints.RData'))
```

@@

```{r download Christensen, eval = F}

paper_filepath <- here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files')
test_filepath <- here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_LDA_analysis.r')

@@

```{r LDATS data}
data(rodents)

head(rodents[[1]])
```

@@

```{r Paper data, eval = F}
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_data_for_LDA.r'))

@@

```{r adjust LDATS data after Christensen et al, eval = F}

trap_table = read.csv('https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/Portal_rodent_trapping.csv')

```{r continue adjust LDATS after paper}
 trap_table_controls =dplyr::filter(trap_table, plot %in% c(2,4,8,11,12,14,17,22))
  nplots_controls = aggregate(trap_table_controls$sampled,by=list(period = trap_table_controls$period),FUN=sum)
   # adjust species counts by number of plots trapped that month
  ldats_rodents_adjusted = as.data.frame.matrix(rodents[[1]])
  for (n in 1:436) {
    #divide by number of control plots actually trapped (should be 8) and multiply by 8 to estimate captures as if all plots were trapped
    ldats_rodents_adjusted[n,] = round(ldats_rodents_adjusted[n,]/nplots_controls$x[n]*8)
  }

@@

@@

#### Paper LDA
```{r plot paper LDA, fig.width=7, fig.height=6}
# Paper
plot(ldamodel, cols = NULL, option = "D")

@@

#### LDATS LDA
```{r plot LDATS LDA, fig.width=7, fig.height=6}
# LDATS
plot(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

@@

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
ldats_paper_cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
save(ldats_paper_cp_results_rodent, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
rm(ldats_paper_cp_results_rodent)

ldats_paper_cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
save(ldats_paper_cp_results_rodent2, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
rm(ldats_paper_cp_results_rodent2)

ldats_paper_cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
save(ldats_paper_cp_results_rodent3, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
rm(ldats_paper_cp_results_rodent3)

ldats_paper_cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
save(ldats_paper_cp_results_rodent4, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
rm(ldats_paper_cp_results_rodent4)

ldats_paper_cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
save(ldats_paper_cp_results_rodent5, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
rm(ldats_paper_cp_results_rodent5)

ldats_paper_cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
save(ldats_paper_cp_results_rodent6, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))
rm(ldats_paper_cp_results_rodent6)
```

```{r select LDATS LDA and paper cpt, eval = F}
#### Changepoint model selection ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))

```{r select LDATS-paper, eval = T}
ntopics = ldats_lda_selected[[1]]@k

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(ldats_paper_cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(ldats_paper_cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(ldats_paper_cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(ldats_paper_cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(ldats_paper_cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(ldats_paper_cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

@@

ldats_paper_cpt_selected = ldats_paper_cp_results_rodent4

df_4 = as.data.frame(t(ldats_paper_cpt_selected$saved[,1,])) %>% reshape::melt()
year_continuous = 1970 + as.integer(julian(paper_dates)) / 365.25
df_4$value = year_continuous[df_4$value]

@@

@@

```{r load paper LDA for paper cpt, eval = F}

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
paper_paper_cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
save(paper_paper_cp_results_rodent, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_1.Rds'))
rm(paper_paper_cp_results_rodent)

paper_paper_cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
save(paper_paper_cp_results_rodent2, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_2.Rds'))
rm(paper_paper_cp_results_rodent2)

paper_paper_cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
save(paper_paper_cp_results_rodent3, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_3.Rds'))
rm(paper_paper_cp_results_rodent3)

paper_paper_cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
save(paper_paper_cp_results_rodent4, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
rm(paper_paper_cp_results_rodent4)

paper_paper_cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
save(paper_paper_cp_results_rodent5, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_5.Rds'))
rm(paper_paper_cp_results_rodent5)

paper_paper_cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
save(paper_paper_cp_results_rodent6, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_6.Rds'))
rm(paper_paper_cp_results_rodent6)
```

```{r select paper LDA and paper cpt, eval = F}
#### Changepoint model selection ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_1.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_2.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_3.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_5.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_6.Rds'))
```

```{r select paper-paper, eval = T}
ntopics = ldamodel@k

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(paper_paper_cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(paper_paper_cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(paper_paper_cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(paper_paper_cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(paper_paper_cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(paper_paper_cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

@@

paper_paper_cpt_selected = paper_paper_cp_results_rodent4

df_4 = as.data.frame(t(paper_paper_cpt_selected$saved[,1,])) %>%  reshape::melt()
df_4$value = year_continuous[df_4$value]

@@

@@

#### Run the TS models

@@

ldats_ldats_cpt <- TS_on_LDA(LDA_models = ldats_lda_selected,
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             weights = NULL,
                             control = TS_controls_list(timename = 'newmoon'))

@@

@@

@@

```{r load paper LDA for LDATS cpt, eval = F}

@@

paper_ldats_cpt <- TS_on_LDA(LDA_models = ldamodel,
                             document_covariate_table = rodents$document_covariate_table,
                             formulas = ~ sin_year + cos_year,
                             nchangepoints = 1:6,
                             weights = NULL,
                              control = TS_controls_list(timename = 'newmoon'))

@@

@@

@@

```{r load cpts to plot, include = F}

@@

```{r plot paper LDA and LDATS cpts, fig.width=7, fig.height=6}

@@

#### LDATS LDA and LDATS changepoint
```{r plot ldats LDA and LDATS cpt, fig.width=7, fig.height=6}
plot(ldats_ldats_cpt_selected)
```

#### Paper LDA and paper changepoint
```{r plot paper LDA and paper cpt, fig.width=7, fig.height=6}

@@

#### LDATS LDA and paper changepoint
```{r plot LDATS lda and paper cpt, fig.width=7, fig.height=6}
ntopics = 6
ldats_cpts = find_changepoint_location(ldats_paper_cpt_selected)
ldats_cpt_plot = get_ll_non_memoized_plot(ldats_lda_selected[[1]],x,ldats_cpts,make_plot=T,weights=rep(1,length(year_continuous)))
annual_hist(ldats_paper_cpt_selected, year_continuous)
ldats_cpt_plot
```

@@
